\documentclass{article}
\usepackage{times}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage{graphicx}
%\usepackage{mathpazo}
\usepackage[hmargin=10em,vmargin=8em]{geometry}
\usepackage{enumerate}
\usepackage{setspace}
\usepackage{listings}
\usepackage{mathrsfs}

%New definition of square root:
% it renames \sqrt as \oldsqrt
\let\oldsqrt\sqrt
% it defines the new \sqrt in terms of the old one
\def\sqrt{\mathpalette\DHLhksqrt}
\def\DHLhksqrt#1#2{%
\setbox0=\hbox{$#1\oldsqrt{#2\,}$}\dimen0=\ht0
\advance\dimen0-0.2\ht0
\setbox2=\hbox{\vrule height\ht0 depth -\dimen0}%
{\box0\lower0.4pt\box2}}

\newcommand{\listfile}[1]{\lstset{caption=#1,basicstyle=\small, breaklines=true, breakatwhitespace=false}
  \lstinputlisting{#1}}
\lstset{language=R, frame=single, breaklines=true}

\newcommand{\lp}{\left (}
\newcommand{\rp}{\right )}


\title {Kitchen Duty Week}
\author{Forskarbacken 17 \\ Floor 2}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}
\begin{abstract}
  When it is your turn to guard the kitchen, maybe you will start to wonder what this duty really means. This is a simple guide to what you should do during this week so that your corridor mates will be happy.
\end{abstract}
\section*{What You Should Try to do Every Day}
\begin{itemize}
\item
  Take out the garbage under the sink and put in new plastic bags in the containers.
\item
  Empty the dish racks.
\item
  Make sure the kitchen counters and the tables are clean.
\item
  Make sure the stoves and ovens are clean.
\end{itemize}
\section*{What You Should do at Least Once During the Week}
\begin{itemize}
\item
  Sweep (or vacuum) the kitchen and corridor floor.
\item
  Clean the floors with wet mop.
\item
  Empty all of the recycling bins (metal/paper/plastic/glass).
\end{itemize}
  
\section*{What Everybody Else Should do}
\begin{itemize}
\item
  Keep it as clean as possible during kitchen use.
\item
  Correctly sort their garbage into the recycling bins.
\item
  Wash up their dishes.
\end{itemize}
\section*{Final Tip}
If you for some reason cannot fulfill your kitchen duties some day/weekend, try to make a deal with some of your corridor mates. Maybe it is possible to trade a kitchen duty day for a dinner/hug or to simply swap weeks.
\subsection*{Final Final Tip}
This document (and its source code) is available at \verb&http://github.com/alneberg/kitchen_duty&, for improvements or additions, a pull request is the recommended way to proceed.

\end{document}
